\textsc{Second-order state-constraint Hamilton-Jacobi equations}

### 2021-05-03 Drafts and notes/Draft_02.tex
New Draft with established results

%============%============%============%============%
%\setlength{\columnseprule}{0.4pt}
%\setlength{\topmargin}{0cm}
%\setlength{\oddsidemargin}{.25cm}
%\setlength{\evensidemargin}{.25cm}
%\setlength{\textheight}{22.5cm}
%\setlength{\textwidth}{15.5cm}
\renewcommand{\baselinestretch}{1.05}
%============%============%============%============%
\usepackage[toc,page]{appendix}
%============%============%============%============%
%\usepackage{romannum}
\usepackage{xcolor}
\usepackage{placeins}
\usepackage{amsfonts,amsmath,amsthm}
\usepackage{amssymb,epsfig}
\usepackage{enumerate} 
\usepackage[notcite,notref]{showkeys}
\usepackage{fullpage}
%============%============%============%============%
\usepackage[utf8]{inputenc}
%\usepackage{mathpazo}

@@

\begin{defn} Let us define
\begin{equation}\label{def:delta_0}
    \delta_{0,\Omega} = \sup \big\{ \delta > 0: x\mapsto\mathrm{dist}(x,\partial\Omega)\;\text{is}\;\rmC^2\;\text{in}\;\Omega\backslash\overline{\Omega}_{\delta} \big\}.
\end{equation}
The distance function is of class $\mathrm{C}^2$ in the region where $0<\mathrm{dist}(x,\partial\Omega) < \delta_0$. We will simply write $\delta_0$ if the underlying domain is understood.
\end{defn}

@@

\begin{lem}\label{lem:lower-bound} Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ be a solution to \eqref{eq:PDEeps}. We have $\{  u^\varepsilon\}_{\varepsilon>0}$ is uniformly bounded from below by a constant independent of $\varepsilon$. Precisely, we have $  u^\varepsilon \geq \min_\Omega f$ and $  u\geq \min_\Omega f$.
%\begin{equation}\label{e:lower_bound_u_eps}
%    \inf_{x\in \Omega}   u^\varepsilon(x) \geq  \inf_{\Omega} f
%\end{equation}
%and also
%\begin{equation}\label{e:lower_bound_u}
%    \inf_{x\in \Omega}   u(x) \geq  \inf_{\Omega} f
%\end{equation}
\end{lem}
\begin{proof} For $m\in \mathbb{N}$, let $u^{\varepsilon,m}\in \mathrm{C}^2(\Omega)\cap \rmC(\overline{\Omega})$ solves the Drichlet problem
\begin{equation}\label{e:uepsm}
    \begin{cases}
      u(x) + |Du(x)|^p - f(x) - \varepsilon \Delta u(x) = 0 &\qquad
    \text{in}\;\Omega, \vspace{0cm}\\
    \;\qquad\quad\qquad\qquad\qquad\qquad u(x) = m &\qquad
    \text{on}\;\partial\Omega.
    \end{cases} \tag{PDE$_{\varepsilon,m}$}
\end{equation}
We have $u^{\varepsilon}_m(x) \to u^\varepsilon(x)$ as $m\to \infty$ in $\Omega$. Let $\varphi(x) \equiv  ^{-1} \inf_{\Omega} f$ for $x\in \overline{\Omega}$ then $\varphi(x)$ is a classical subsolution of \eqref{e:uepsm} in $\Omega$ with
\begin{equation*}
    \varphi(x) =   \inf_\Omega f \leq m = u^\varepsilon_m(x) \qquad\text{for}\;x\in \partial\Omega.
\end{equation*}
By comparison principle for the uniformly elliptic equation \eqref{e:uepsm} we have
\begin{equation*}
     ^{-1}\inf_\Omega f \leq u^{\varepsilon}_m(x) \qquad\text{for all}\;x\in \Omega.
\end{equation*}
As $m\to \infty$ we obtain $  u^\varepsilon \geq \min_\Omega f$. The inequality $  u\geq \min_{\Omega}f$ follows from the comparison principle of \eqref{eq:PDE0} between supersolution $u$ on $\overline{\Omega}$ and subsolution $\varphi(x)$ in $\Omega$.
\end{proof}

@@

\begin{proof}[Proof of Theorem \ref{thm:qual}] By a priori estimate (Theorem \ref{thm:grad_1}) we have
\begin{equation}\label{e:priorie_eps}
    |u^\varepsilon(x)| + |Du^\varepsilon(x)| \leq C_\delta \qquad\text{for}\;x\in \overline{\Omega}_\delta
\end{equation}
we deduce from the Arzel\'a--Ascoli theorem that there exists a subsequence $\varepsilon_j\to 0$ and a function $u\in \rmC(\Omega)$ such that $u^{\varepsilon_j}\to u$ locally uniformly in $\Omega$. By the stability of viscosity solution we easily deduce that 
\begin{equation}\label{eq:u0int}
     u(x) + |Du(x)| - f(x) = 0 \qquad\text{in}\;\Omega.
\end{equation}
From Lemma \ref{lem:lower-bound} we have $  u^\varepsilon(x)\geq \min_{\Omega} f$ and  $  u(x)\geq \min_{\Omega} f$ for all $x\in \Omega$, together with \eqref{eq:u0int} we obtain $|\xi|\leq \max_\Omega f - \min_\Omega f$ for all $\xi\in D^+u(x)$ and $x\in \Omega$. In other words there is a constant $C_0$ such that
\begin{equation*}
    |u(x) - u(y)| \leq C_0|x-y| \qquad\text{for all}\;x,y\in \Omega.
\end{equation*}
Thus we can extend $u$ uniquely to $u\in \rmC(\overline{\Omega})$. We will use Lemma \ref{lem:max} to show that $u$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$. It suffices to show that $u\geq w$ on $\overline{\Omega}$ where $w\in \rmC(\overline{\Omega})$ is the unique solution to \eqref{eq:PDE0}.

@@

\section{Rate of convergence via the doubling variables method}
In this section, we focus on the rate of convergence for the case $f\in \mathrm{C}^1(\overline{\Omega})$. By adding a constant to the solution $u^\varepsilon$ of \eqref{eq:PDEeps}, without loss of generality we can assume the \emph{nonnegativity}
\begin{equation}\label{e:minf}
    \min_{\overline{\Omega}} f(x) = 0.
\end{equation}
As a consequence, $u^\varepsilon(x),u(x)\geq 0$ for $x\in \Omega$ by Lemma \ref{lem:lower-bound}.
\subsection{Lower bound}
We start with the lower bound of $u^\varepsilon - u$.
\begin{thm} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary. Assume \eqref{e:minf} and $H(x,\xi) = |\xi|^p - f(x)$ where $p\in\left(1,2\right]$. Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}, then there exists a constant $C$ independent of $\varepsilon$ such that
\begin{equation}\label{e:lower1}
    -C\sqrt{\varepsilon} \leq u^\varepsilon(x) - u(x) \qquad\text{for all}\;x\in \Omega.
\end{equation} 
\end{thm}
\begin{proof} The proof relies on a well-known rate of convergence for vanishing viscosity of viscous Hamilton--Jacobi equation with Dirichlet boundary condition (\textcolor{blue}{citation}). As $u\in \mathrm{C}(\overline{\Omega})$, let $g(x) = u(x)$ for $x\in \partial\Omega$ then $g\in \mathrm{C}(\partial\Omega)$. Let $v^\varepsilon\in \mathrm{C}^2(\Omega)\cap \mathrm{C}(\overline{\Omega})$ be the unique viscosity solution to
\begin{equation*}
    \begin{cases}
          v^\varepsilon(x) + |Dv^\varepsilon(x)|^p - f(x) - \varepsilon \Delta v^\varepsilon(x) = 0 &\qquad\text{in}\;\Omega,\\
        \qquad\qquad\qquad\qquad\qquad \qquad\quad v^\varepsilon(x) = g(x) &\qquad\text{on}\;\partial\Omega.
    \end{cases}
\end{equation*}
It is well-known that $v^\varepsilon \to u$ uniformly where $v$ is the viscosity solution to
\begin{equation*}
\begin{cases}
       v(x) + |Dv(x)| - f(x) = 0 &\qquad\text{in}\;\Omega,\\
     \qquad\qquad\qquad\quad\; v(x) = g(x)&\qquad\text{on}\;\partial\Omega. 
\end{cases}
\end{equation*}
By comparison principle, it is clear that $v = u$, the solution of \eqref{eq:PDE0}. Furthermore, there exists a positive constant $C$ such that 
\begin{equation}\label{e:cp1}
     |v^\varepsilon(x)  - u(x)| \leq C\sqrt{\varepsilon} \qquad\text{for}\;x\in \overline{\Omega}.
\end{equation}
By comparison principle for \eqref{eq:PDEeps} we have
\begin{equation}\label{e:cp2}
    v^\varepsilon(x)\leq u^\varepsilon(x) \qquad\text{for}\;x\in \Omega.
\end{equation}
From \eqref{e:cp1} and \eqref{e:cp2} we obtain the lower bound \eqref{e:lower1}.
\end{proof}

@@

\begin{lem}\label{lem:f=0} If $f\geq 0$ in $\Omega$ then $u(x) = 0$ whenever $f(x) = 0$. In particular $f \equiv 0$ implies $u \equiv 0$.
\end{lem}
\begin{proof} We have $u\geq 0$ in $\overline{\Omega}$. Using the optimal control formula (\cite{Bardi1997,Hung2019}), we have
\begin{equation}\label{e:foru}
    u(x) = \inf \left\lbrace \int_0^\infty e^{-  s}\Big(c|\dot{\eta}(s)|^{q} +f(\eta(s))\Big)ds: \eta\in \mathrm{AC}([0,\infty);\overline{\Omega}), \eta(0) = x\right\rbrace
\end{equation}
where 
\begin{equation*}
    c = \left(pq^{\frac{1}{p-1}}\right)^{-1} \qquad\text{and}\qquad \frac{1}{p} + \frac{1}{q} = 1.
\end{equation*}
Assume that $f(x) = 0$, we can choose $\eta(s) = x$ for all $s\in [0,\infty)$ as an admissible path in \eqref{e:foru} to obtain that
\begin{equation*}
    u(x) \leq  \int_0^\infty e^{-  s}\Big(c|\dot{\eta}(s)|^{q} +f(\eta(s))\Big)ds = f(x) =  0.
\end{equation*}
\end{proof}
\noindent For simplicity, let us assume $  = 1$ from now on. We state the following lemma as a crucial estimate we will be using. It is a refined construction of the supersolution for \eqref{eq:PDEeps}.
\begin{lem}\label{lem:super_refined} There exist positive constants $\nu = \nu(\alpha,\delta_0)$ and $C_\nu$ such that if $0\leq \delta \leq \frac{1}{2}\delta_0$ then
\begin{equation*}
    w(x) = \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + \max f + C_\nu \varepsilon^{\alpha+2}, \qquad x\in \Omega_\delta 
\end{equation*}
is a supersolution of \eqref{eq:PDEeps} in $\Omega_\delta$. 
\end{lem}

\begin{proof}
We have $|\nabla d(x)| = 1$ for all $x\in \Omega_\delta\backslash \Omega_{\delta_0}$. Recall from Theorem \ref{thm:wellposed1<p<2} that $C_\alpha^p \alpha^p = C_\alpha \alpha (\alpha+1)$ and $p(\alpha+1) = \alpha+2$, we compute 
\begin{equation*}
    |\nabla w(x)|^p = \nu^p\frac{(C_\alpha\alpha)^p\varepsilon^{p(\alpha+1)}}{(d(x)-\delta)^{p(\alpha+1)}} = \nu^p\frac{C_\alpha \alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}
\end{equation*}
and
\begin{equation*}
    \varepsilon\Delta w(x) = \nu\frac{C_\alpha\alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}} - \nu\frac{C_\alpha\alpha\varepsilon^{\alpha+2}\Delta d(x)}{(d(x)-\delta)^{\alpha+1}}.
\end{equation*}
We have
\begin{equation*}
    \begin{split}
        \mathcal{L}\left[w_\delta\right] \geq \frac{\nu C_\alpha\varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + \frac{C_\alpha \alpha (\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}\left[\nu^p-\nu +\nu\frac{(d(x)-\delta)\Delta d(x)}{\alpha+1}\right].
    \end{split}
\end{equation*}
Recall that $K_2= \Vert \Delta d\Vert_{L^\infty}$, we observe that in the region where $\delta< d(x)\leq \delta_0$ then
\begin{equation*}
    \left|\frac{(d(x)-\delta)\Delta d(x)}{\alpha+1}\right| \leq \frac{\delta_0\Vert \Delta d\Vert_{L^\infty}}{\alpha+1} \leq \frac{K_2\delta_0}{\alpha+1}\leq K_2\delta_0.
\end{equation*}
Therefore
\begin{equation}\label{e:choose_nu}
    \begin{split}
        \nu^p-\nu +\nu\frac{(d(x)-\delta)\Delta d(x)}{(\alpha+1)} \geq \nu^p - \nu - \nu K_2\delta_0 = \nu\Big(\nu^{p-1} - (1+K_2\delta_0)\Big).
    \end{split}
\end{equation}
We will choose $\nu$ as follows. For $\gamma>1$ we have
\begin{equation*}
    \Big||x+y|^\gamma - |x|^\gamma\Big|\leq \gamma\Big(|x|+|y|\Big)^{\gamma-1}|y|
\end{equation*}
which implies that
\begin{equation*}
     0 \leq (1+K_2\delta_0)^{\alpha+1} - 1 \leq\underbrace{(\alpha+1)\left(1+K_2\delta_0\right)^\alpha K_2}_{C_2}\delta_0.
\end{equation*}
which implies that $(1+K_2\delta_0)^{\alpha+1} \leq 1 + C_2\delta_0$, thus
\begin{equation}\label{e:cru1}
    (1+K_2\delta_0) \leq (1+C_2\delta_0)^{\frac{1}{\alpha+1}} = (1+C_2\delta_0)^{p-1}
\end{equation}
since $\alpha+1 = \frac{1}{p-1}$. Choose $\nu = 1+C_2\delta_0$ in \eqref{e:choose_nu} we obtain $\mathcal{L}[w]\geq 0$ in $\{x\in \Omega_\delta: \delta <d(x)\leq \delta_0\}$. Recall that $K_0 = \Vert d\Vert_{L^\infty}$ and $K_1 = \Vert \nabla d\Vert_{L^\infty}$. In the region where $d(x)\geq \delta_0$ then $d(x)-\delta \geq \frac{1}{2}\delta_0$, we have 
\begin{align*}
    \mathcal{L}[w] &= \frac{\nu C_\alpha\alpha\varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + \max_{\Omega} f - f(x)\\
    &+  \nu^p\frac{C_\alpha\alpha(\alpha+1)\varepsilon^{\alpha+1}}{(d(x)-\delta)^{\alpha+2}}|\nabla d(x)|^p - \nu \frac{C_\alpha \alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}|\nabla d(x)|^2 
    + \nu \frac{C_\alpha \alpha \varepsilon^{\alpha+2}\Delta d(x)}{(d(x)-\delta)^{\alpha+1}} + C_\nu \varepsilon^{\alpha+2}\\
    &\geq \frac{C_\alpha \alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}\left(\nu^p|\nabla d(x)|^p - \nu |\nabla d(x)|^2 + \nu \frac{\Delta d(x)(d(x)-\delta)}{\alpha+1}\right) + C_\nu \varepsilon^{\alpha+2}\\
    &\geq (C_\nu - C_3)\varepsilon^{\alpha+2}
\end{align*}
where 
\begin{equation*}
    C_3 = \left(\frac{2}{\delta_0}\right)^{\alpha+2} C_\alpha\alpha(\alpha+1) \left(\nu^pK_1^p + \nu K_1^2 + \nu \frac{K_0K_2}{\alpha+1}\right).
\end{equation*}
Therefore we can choose $C_\nu = C_3$ to obtain $\mathcal{L}[w]\geq 0$ in this region $\{x\in \Omega_\delta:d(x)\geq \delta_0\}$.
\end{proof}

\subsection{Zero data}
\begin{thm}\label{thm:rate_doubling0} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary. Assume that $H(x,\xi) = |\xi|^p - f(x)$ where $p\in\left(1,2\right)$ and $f\equiv 0$ in $\Omega$. Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u \equiv 0 $ be the unique solution to \eqref{eq:PDE0}. Then there exists a constant $C$ independent of $\varepsilon$ such that
\begin{equation*}
 -C \varepsilon^{\frac{1}{2}}\leq  u^\varepsilon(x) - u(x) \leq C\varepsilon \quad  \text{for} \quad x\in \Omega_{\varepsilon}.
\end{equation*}
\end{thm}

>>>>

%============%============%============%============%
%\setlength{\columnseprule}{0.4pt}
%\setlength{\topmargin}{0cm}
%\setlength{\oddsidemargin}{.25cm}
%\setlength{\evensidemargin}{.25cm}
%\setlength{\textheight}{22.5cm}
%\setlength{\textwidth}{15.5cm}
\renewcommand{\baselinestretch}{1.05}
%============%============%============%============%
\usepackage[toc,page]{appendix}
%\setcounter{secnumdepth}{4}
%\setcounter{tocdepth}{3}
%============%============%============%============%
%\usepackage{romannum}
\usepackage{xcolor}
\usepackage{placeins}
\usepackage{amsfonts,amsmath,amsthm}
\usepackage{amssymb,epsfig}
\usepackage{enumerate} 
\usepackage[notcite,notref]{showkeys}
\usepackage{fullpage}
%============%============%============%============%
\usepackage[utf8]{inputenc}
%\usepackage{mathpazo}

@@

\begin{defn} Let us define
\begin{equation}\label{def:delta_0}
    \delta_{0,\Omega} = \frac{1}{2}\sup \big\{ \delta > 0: x\mapsto\mathrm{dist}(x,\partial\Omega)\;\text{is}\;\rmC^2\;\text{in}\;\Omega\backslash\overline{\Omega}_{\delta} \big\}.
\end{equation}
%The distance function is of class $\mathrm{C}^2$ in the region where $0<\mathrm{dist}(x,\partial\Omega) < \delta_0$. 
We will simply write $\delta_0$ instead of $\delta_{0,\Omega}$ if the underlying domain is understood.
\end{defn}

@@

\begin{lem}\label{lem:lower-bound} Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ be a solution to \eqref{eq:PDEeps}. We have $\{  u^\varepsilon\}_{\varepsilon>0}$ is uniformly bounded from below by a constant independent of $\varepsilon$. Precisely, we have $  u^\varepsilon \geq \min_\Omega f$ and $  u\geq \min_\Omega f$.
%\begin{equation}\label{e:lower_bound_u_eps}
%    \inf_{x\in \Omega}   u^\varepsilon(x) \geq  \inf_{\Omega} f
%\end{equation}
%and also
%\begin{equation}\label{e:lower_bound_u}
%    \inf_{x\in \Omega}   u(x) \geq  \inf_{\Omega} f
%\end{equation}
\end{lem}
\begin{proof} For $m\in \mathbb{N}$, let $u^{\varepsilon,m}\in \mathrm{C}^2(\Omega)\cap \rmC(\overline{\Omega})$ solves the Drichlet problem
\begin{equation}\label{e:uepsm}
    \begin{cases}
      u(x) + |Du(x)|^p - f(x) - \varepsilon \Delta u(x) = 0 &\qquad
    \text{in}\;\Omega, \vspace{0cm}\\
    \;\qquad\quad\qquad\qquad\qquad\qquad u(x) = m &\qquad
    \text{on}\;\partial\Omega.
    \end{cases} \tag{PDE$_{\varepsilon,m}$}
\end{equation}
We have $u^{\varepsilon}_m(x) \to u^\varepsilon(x)$ as $m\to \infty$ in $\Omega$. Let $\varphi(x) \equiv  \inf_{\Omega} f$ for $x\in \overline{\Omega}$ then $\varphi(x)$ is a classical subsolution of \eqref{e:uepsm} in $\Omega$ with
\begin{equation*}
    \varphi(x) =   \inf_\Omega f \leq m = u^\varepsilon_m(x) \qquad\text{for}\;x\in \partial\Omega.
\end{equation*}
By comparison principle for the uniformly elliptic equation \eqref{e:uepsm} we have
\begin{equation*}
     \inf_\Omega f \leq u^{\varepsilon}_m(x) \qquad\text{for all}\;x\in \Omega.
\end{equation*}
As $m\to \infty$ we obtain $  u^\varepsilon \geq \min_\Omega f$. The inequality $  u\geq \min_{\Omega}f$ follows from the comparison principle of \eqref{eq:PDE0} between supersolution $u$ on $\overline{\Omega}$ and subsolution $\varphi(x)$ in $\Omega$.
\end{proof}

@@

\begin{proof}[Proof of Theorem \ref{thm:qual}] By a priori estimate (Theorem \ref{thm:grad_1}) we have
\begin{equation}\label{e:priorie_eps}
    |u^\varepsilon(x)| + |Du^\varepsilon(x)| \leq C_\delta \qquad\text{for}\;x\in \overline{\Omega}_\delta
\end{equation}
we deduce from the Arzel\'a--Ascoli theorem that there exists a subsequence $\varepsilon_j\to 0$ and a function $u\in \rmC(\Omega)$ such that $u^{\varepsilon_j}\to u$ locally uniformly in $\Omega$. By the stability of viscosity solution we easily deduce that 
\begin{equation}\label{eq:u0int}
     u(x) + |Du(x)| - f(x) = 0 \qquad\text{in}\;\Omega.
\end{equation}
From Lemma \ref{lem:lower-bound} we have $  u^\varepsilon(x)\geq \min_{\Omega} f$ and  $  u(x)\geq \min_{\Omega} f$ for all $x\in \Omega$, together with \eqref{eq:u0int} we obtain $|\xi|\leq \max_\Omega f - \min_\Omega f$ for all $\xi\in D^+u(x)$ and $x\in \Omega$. In other words there is a constant $C_0$ such that
\begin{equation}\label{e:C0}
    |u(x) - u(y)| \leq C_0|x-y| \qquad\text{for all}\;x,y\in \Omega.
\end{equation}
Thus we can extend $u$ uniquely to $u\in \rmC(\overline{\Omega})$. We will use Lemma \ref{lem:max} to show that $u$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$. It suffices to show that $u\geq w$ on $\overline{\Omega}$ where $w\in \rmC(\overline{\Omega})$ is the unique solution to \eqref{eq:PDE0}.

@@

\section{Rate of convergence via the doubling variables method}
In this section, we focus on the rate of convergence for the case $f\in \mathrm{Lip}(\Omega)\cap\mathrm{C}^(\overline{\Omega})$. By adding a constant to the solution $u^\varepsilon$ of \eqref{eq:PDEeps}, without loss of generality we can assume the \emph{nonnegativity}
\begin{equation}\label{e:minf}
    \min_{\overline{\Omega}} f(x) = 0.
\end{equation}
As a consequence, $u^\varepsilon(x),u(x)\geq 0$ for $x\in \Omega$ by Lemma \ref{lem:lower-bound}.
\subsection{Lower bound}
We start with the lower bound of $u^\varepsilon - u$.
\begin{thm} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary. Assume \eqref{e:minf} and $H(x,\xi) = |\xi|^p - f(x)$ where $p\in\left(1,2\right]$. Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}, then there exists a constant $C$ independent of $\varepsilon$ such that
\begin{equation}\label{e:lower1}
    -C\sqrt{\varepsilon} \leq u^\varepsilon(x) - u(x) \qquad\text{for all}\;x\in \Omega.
\end{equation} 
\end{thm}
\begin{proof} The proof relies on a well-known rate of convergence for vanishing viscosity of viscous Hamilton--Jacobi equation with Dirichlet boundary condition (\textcolor{blue}{citation}). As $u\in \mathrm{C}(\overline{\Omega})$, let $g(x) = u(x)$ for $x\in \partial\Omega$ then $g\in \mathrm{C}(\partial\Omega)$. Let $v^\varepsilon\in \mathrm{C}^2(\Omega)\cap \mathrm{C}(\overline{\Omega})$ be the unique viscosity solution to
\begin{equation*}
    \begin{cases}
          v^\varepsilon(x) + |Dv^\varepsilon(x)|^p - f(x) - \varepsilon \Delta v^\varepsilon(x) = 0 &\qquad\text{in}\;\Omega,\\
        \qquad\qquad\qquad\qquad\qquad \qquad\quad v^\varepsilon(x) = g(x) &\qquad\text{on}\;\partial\Omega.
    \end{cases}
\end{equation*}
It is well-known that $v^\varepsilon \to u$ uniformly where $v$ is the viscosity solution to
\begin{equation*}
\begin{cases}
       v(x) + |Dv(x)|^p - f(x) = 0 &\qquad\text{in}\;\Omega,\\
     \qquad\qquad\qquad\quad\;\;\; v(x) = g(x)&\qquad\text{on}\;\partial\Omega. 
\end{cases}
\end{equation*}
By comparison principle, it is clear that $v = u$, the solution of \eqref{eq:PDE0}. Furthermore, there exists a positive constant $C$ such that 
\begin{equation}\label{e:cp1}
     |v^\varepsilon(x)  - u(x)| \leq C\sqrt{\varepsilon} \qquad\text{for}\;x\in \overline{\Omega}.
\end{equation}
By comparison principle for \eqref{eq:PDEeps} we have
\begin{equation}\label{e:cp2}
    v^\varepsilon(x)\leq u^\varepsilon(x) \qquad\text{for}\;x\in \Omega.
\end{equation}
From \eqref{e:cp1} and \eqref{e:cp2} we obtain the lower bound \eqref{e:lower1}.
\end{proof}

@@

\begin{lem}\label{lem:f=0} Assume $f\geq 0$ in $\Omega$ then $u(x) = 0$ whenever $f(x) = 0$. In particular $f \equiv 0$ implies $u \equiv 0$.
\end{lem}
\begin{proof} It is clear that $u\geq 0$ in $\overline{\Omega}$. Using the optimal control formula (see \cite{Bardi1997,Hung2019}), we have
\begin{equation}\label{e:foru}
    u(x) = \inf \left\lbrace \int_0^\infty e^{-  s}\Big(c|\dot{\eta}(s)|^{q} +f(\eta(s))\Big)ds: \eta\in \mathrm{AC}([0,\infty);\overline{\Omega}), \eta(0) = x\right\rbrace
\end{equation}
where 
\begin{equation*}
    c = \left(pq^{\frac{1}{p-1}}\right)^{-1} \qquad\text{and}\qquad \frac{1}{p} + \frac{1}{q} = 1.
\end{equation*}
Let $x\in \overline{\Omega}$ such that $f(x) = 0$, we can choose $\eta(s) = x$ for all $s\in [0,\infty)$ as an admissible path in \eqref{e:foru} to obtain that
\begin{equation*}
    u(x) \leq  \int_0^\infty e^{-  s}\Big(c|\dot{\eta}(s)|^{q} +f(\eta(s))\Big)ds = f(x) =  0.
\end{equation*}
As a consequence if $f\equiv 0$ then $u\equiv 0$.
\end{proof}
\noindent We state the following lemma as a crucial estimate we will be using. It is a refined construction of the supersolution for \eqref{eq:PDEeps}.
\begin{lem}\label{lem:super_refined} Let $\delta_0$ be defined as in \eqref{def:delta_0}. 
\begin{itemize}
    \item[(i)] There exist positive constants $\nu = \nu(\delta_0) \in (1,2)$ and $C_\nu =\mathcal{O}\left(\delta_0^{-(\alpha+2)}\right)$ such that, if $0\leq \delta <\frac{1}{2}\delta_0$ then
\begin{equation}\label{e:superwa}
    w(x) = \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + \max f + C_\nu \varepsilon^{\alpha+2}, \qquad x\in \Omega_\delta 
\end{equation}
is a supersolution of \eqref{eq:PDEeps} in $\Omega_\delta$. 
\item[(ii)] If $x\mapsto \mathrm{dist}(x,\partial\Omega)$ is continuously differentiable with $|\nabla \mathrm{dist}(x,\partial\Omega)| = 1$ everywhere in $\Omega$ then we can take $C_\nu = 0$ in \eqref{e:superwa}.
\end{itemize}
\end{lem}

\begin{proof} We have $|\nabla d(x)| = 1$ for all $x\in \Omega_\delta\backslash \overline{\Omega}_{\delta_0}$. Recall from Theorem \ref{thm:wellposed1<p<2} that $C_\alpha^p \alpha^p = C_\alpha \alpha (\alpha+1)$ and $p(\alpha+1) = \alpha+2$, we compute 
\begin{equation*}
    |\nabla w(x)|^p = \nu^p\frac{(C_\alpha\alpha)^p\varepsilon^{p(\alpha+1)}}{(d(x)-\delta)^{p(\alpha+1)}} = \nu^p\frac{C_\alpha \alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}
\end{equation*}
and
\begin{equation*}
    \varepsilon\Delta w(x) = \nu\frac{C_\alpha\alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}} - \nu\frac{C_\alpha\alpha\varepsilon^{\alpha+2}\Delta d(x)}{(d(x)-\delta)^{\alpha+1}}.
\end{equation*}
We have
\begin{equation*}
    \begin{split}
        \mathcal{L}^\varepsilon\left[w_\delta\right] \geq \frac{\nu C_\alpha\varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + \frac{C_\alpha \alpha (\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}\left[\nu^p-\nu +\nu\frac{(d(x)-\delta)\Delta d(x)}{\alpha+1}\right].
    \end{split}
\end{equation*}
Recall that $K_2= \Vert \Delta d\Vert_{L^\infty}$, we observe that in the region where $\delta< d(x)\leq \delta_0$ then
\begin{equation*}
    \left|\frac{(d(x)-\delta)\Delta d(x)}{\alpha+1}\right| \leq \frac{\delta_0\Vert \Delta d\Vert_{L^\infty}}{\alpha+1} \leq \frac{K_2\delta_0}{\alpha+1}\leq K_2\delta_0.
\end{equation*}
Therefore
\begin{equation}\label{e:choose_nu}
    \begin{split}
        \nu^p-\nu +\nu\frac{(d(x)-\delta)\Delta d(x)}{(\alpha+1)} \geq \nu^p - \nu - \nu K_2\delta_0 = \nu\Big(\nu^{p-1} - (1+K_2\delta_0)\Big).
    \end{split}
\end{equation}
We will choose $\nu$ as follows. For $\gamma>1$ we have the inequality
\begin{equation*}
    \Big||x+y|^\gamma - |x|^\gamma\Big|\leq \gamma\Big(|x|+|y|\Big)^{\gamma-1}|y|
\end{equation*}
for $x,y\in \mathbb{R}$, which implies that
\begin{equation*}
     0 \leq (1+K_2\delta_0)^{\alpha+1} - 1 \leq\underbrace{(\alpha+1)\left(1+K_2\delta_0\right)^\alpha K_2}_{C_2}\delta_0.
\end{equation*}
which implies that $(1+K_2\delta_0)^{\alpha+1} \leq 1 + C_2\delta_0$, thus
\begin{equation}\label{e:cru1}
    (1+K_2\delta_0) \leq (1+C_2\delta_0)^{\frac{1}{\alpha+1}} = (1+C_2\delta_0)^{p-1}
\end{equation}
since $\alpha+1 = \frac{1}{p-1}$. Choose $\nu = 1+C_2\delta_0$ in \eqref{e:choose_nu} we obtain $\mathcal{L}[w]\geq 0$ in $\{x\in \Omega_\delta: \delta <d(x)\leq \delta_0\}$. Recall that $K_0 = \Vert d\Vert_{L^\infty}$ and $K_1 = \Vert \nabla d\Vert_{L^\infty}$. In the region where $d(x)\geq \delta_0$ then $d(x)-\delta \geq \frac{1}{2}\delta_0$, we have 
\begin{align*}
    \mathcal{L}[w] &= \frac{\nu C_\alpha\alpha\varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + \max_{\Omega} f - f(x)\\
    &+  \nu^p\frac{C_\alpha\alpha(\alpha+1)\varepsilon^{\alpha+1}}{(d(x)-\delta)^{\alpha+2}}|\nabla d(x)|^p - \nu \frac{C_\alpha \alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}|\nabla d(x)|^2 
    + \nu \frac{C_\alpha \alpha \varepsilon^{\alpha+2}\Delta d(x)}{(d(x)-\delta)^{\alpha+1}} + C_\nu \varepsilon^{\alpha+2}\\
    &\geq \frac{C_\alpha \alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}\left(\nu^p|\nabla d(x)|^p - \nu |\nabla d(x)|^2 + \nu \frac{\Delta d(x)(d(x)-\delta)}{\alpha+1}\right) + C_\nu \varepsilon^{\alpha+2}\\
    &\geq (C_\nu - C_3)\varepsilon^{\alpha+2}
\end{align*}
where 
\begin{equation*}
    C_3 = \left(\frac{2}{\delta_0}\right)^{\alpha+2} C_\alpha\alpha(\alpha+1) \left(\nu^pK_1^p + \nu K_1^2 + \nu \frac{K_0K_2}{\alpha+1}\right).
\end{equation*}
Therefore we can choose $C_\nu = C_3$ to obtain $\mathcal{L}[w]\geq 0$ in this region $\{x\in \Omega_\delta:d(x)\geq \delta_0\}$.

For (ii), we have $d(x) = \mathrm{dist}(x,\partial\Omega)$ (without any smooth mollification away from the boundary) then $|\nabla d(x)| = 1$ for all $x\in \Omega_\delta$, therefore the above proof carries out the same as in \eqref{e:choose_nu} without the need to consider $x$ away from the boundary.
\end{proof}
